---
title: "Informative Title"
author: "Your Name - Your Student Number"
date: June 18, 2021
output:
  pdf_document: default
---

```{r, include=FALSE}
knitr::opts_chunk$set(warning = FALSE, message = FALSE)
library(openintro)
```



# Abstract

<Here you should put a summary of the entire report. You should write the section at the end (i.e., after finishing the other 5 main sections).>



# Introduction

<Here you should have a few paragraphs of text introducing the problem, getting the reader interested/ready for the rest of the report.>

<Introduce terminology.>

<Highlight hypotheses.>

<Optional: You can also include a description of each section of this report as a last paragraph.>


# Data

## Data Collection Process

<Here goes a paragraph describing the data collection process.> 

<Be sure to identify any forseeable drawbacks, limitations, biases, etc.>

<If you created a survey you can describe/showcase the survey here too. Be sure to put the actual survey in the Appendix and a link to it too.>



## Data Summary

<Type here a paragraph introducing the data and its context.>

```{r, include = FALSE}

# Here you can load in and clean the data (you may need to do the cleaning in a separate R script). 

# You may need additional chunks, in case you want to include some of the cleaning output.

```

<Type here a summary of the cleaning process.> 

<Remember, you may want to use multiple datasets here, if you do end up using multiple data sets, or merging the data, be sure to describe this in the cleaning process and be sure to discuss important aspects of all the data that you used.>

<Include a description of the important variables.> 

```{r, include=FALSE}

# Use this to calculate some summary measures. 

```


<Include a description of the numerical summaries. Remember you can use `r ` to use inline R code.>

```{r, echo = TRUE}

# Use this to create some plots. 

```

<Include a clear description of the plot(s). I would recommend one paragraph for each plot.> 

All analysis for this report was programmed using `R version 4.0.4`.


# Methods

<Include some text introducing the methodology as an overall intro to this section.>

<Note, you should have some justification for methods and make sure to relay any assumptions. Be sure to cite any external sources.>

<Add in descriptions of any other methdologies you use. If you are using subtitles, then use more subtitles for these subsections.> 


# Results 

<A paragraph introducing the the overall results.>


```{r, include = FALSE}

# Here you can run your methods


```

<Here you could present your results. You may want to put them into a well formatted table. Be sure that there is some text describing the results, tables and/or plots.>

```{r, include =TRUE}


## Maybe create a nice plot to showcase the results.



```

<Maybe you want to describe your plot. Hint, hint...>


<Note: Alternatively you can use the `knitr::kable` function to create a well formatted table from your code. See here: [https://rmarkdown.rstudio.com/lesson-7.html](https://rmarkdown.rstudio.com/lesson-7.html).>


<Remember you can use `r ` to use inline R code.>

<Include an explanation/interpretation of the visualizations. Make sure to comment on the appropriateness of the assumptions/results.>

# Conclusions

<Here you should give a summary of the Hypotheses, Methods and Results>

<Highlight Key Results.>

<Talk about big picture.>

## Weaknesses

<Comment on any Weaknesses. Note, you are making a lot of assumptions in the MLE and posterior derivations. There is likely to be weaknesses in this. Perhaps having prior info would have been helpful. Perhaps, a more sophisticated Bayesian approach (that we havent learned about in STA238, but you might learn about in a senior level stats course) was needed.>

## Next Steps
<Comment on Future Work/Next Steps/Recommendations.>

## Discussion

<End with a concluding paragraph to wrap up the report.>


# Bibliography

1. Grolemund, G. (2014, July 16) *Introduction to R Markdown*. RStudio. [https://rmarkdown.rstudio.com/articles_intro.html](https://rmarkdown.rstudio.com/articles_intro.html). (Last Accessed: January 15, 2021) 

2. Dekking, F. M., et al. (2005) *A Modern Introduction to Probability and Statistics: Understanding why and how.* Springer Science & Business Media.

3.  Allaire, J.J., et. el. *References: Introduction to R Markdown*. RStudio. [https://rmarkdown.rstudio.com/docs/](https://rmarkdown.rstudio.com/docs/). (Last Accessed: January 15, 2021) 

\newpage

# Appendix

## Section 1 (Maybe call this "Supplementary Data" or "Survey")

<Include your a well formatted glimpse of your data here.>

<Include a link to the survey.>

<Include a complete copy of the survey here (i.e., a list of all questions and options/categories.)>

## Section 2 (Maybe call this "Supplementary Methods" or "Supplementary Plots")

<Include any supplementary plots/methodologies/maths here.>
